\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-03 doc/sw-system.tex
Drafted performance section of discussion #44

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
\caption{Stage 2 agent properties, separating veterans from stage 1 from new
volunteers. Point size represents total information generated, dashed lines
are drawn at the mean values for each sample.}
\label{fig:crowd:stage1vstage2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We now look at the transition between stage 1 and stage 2 in more detail. Of
the 1964 volunteers who took part in the stage 2 classification round, only
774 were veterans from stage 1. However, these volunteers showed significantly
higher skill levels than the new users, and also made more classifications
(and hence made greater contributions. This is illustrated in  
\Fref{fig:crowd:stage1vstage2}. In this figure, point size is proportional to
information generated: the higher skill, higher effort stage 1 veterans
generated most of the information.

@@

Preamble. Notes for future. Improvements to system to be investigated.

@@

Incompleteness, false negatives. Examples and trajectories, from stage 2
training set. Generic properties: hard to spot? Or unlucky? Costly mistakes by
expert classifiers? Or random walk?

Impurity, false positives. Examples and trajectories, from stage 2
training set. Generic properties. Could also be solved by dynamical
stage 2? Improve training?

Solutions: dynamical stage 2, to reduce noise. Does stage 1 skill correlate
with stage 2 skill? Missing group-scale lenses at stage 2. Improve training?
Educational interventions?

>>>>

@@

What can we learn from the results of the previous section, for future
projects? Potential improvements to the \sw system can be divided into three
categories, performance, efficiency and capacity.

@@

We first investigate the source of the incompleteness visible in 
\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives.
\Fref{fig:discuss:performance:FNgallery} shows N example simulated lenses that
were missed by the \sw system. In some cases their rejection is
understandable: the lensed features are faint, or otherwise difficult to see.
However, in other cases a reasonably obvious lens was passed over. 
\Fref{fig:discuss:performance:FNtrajectories} shows the probability 
trajectories of these subjects. \todo{Phil}{Make the FN plots, and look for
behaviour. Can we see whether the FNs are due to costly mistakes by expert
classifiers? Or are they just random walking south?}

Is the system's impurity a result of the same behaviour?
Figures~\ref{fig:discuss:performance:FPgallery}
and~\ref{fig:discuss:performance:FPtrajectories} show the corresponding
figures for the false positives -- non-lenses that were incorrectly inferred
to be lens candidates during stage 2. \todo{Phil}{Make the FP plots, and look
for behaviour. Can we see whether the FPs are due to costly mistakes by expert
classifiers? Or are they just random walking south?}

In general, there are three places we can act to improve system performance:
educating the volunteers, assigning subjects for classification, and
interpreting the classification data. The plots in this section suggest that
...

Mistakes by reasonably high skill classifiers cause large jumps in subject
probability in the wrong direction, as are occasionally visible in the
trajectory plots in this section. We might wonder whether some of those
mistakes could have been corrected by the classifiers themselves, had they had
access to a ``go back'' option. While clearly enabling error reduction, we
might worry about such a mechanism enabling classifiers to have a guess, then
go and read the Talk discussion, and then return to the classification
interface to change their mind to agree with the forum. In fact, this is
already possible on the current interface -- and indeed, it is not obvious
that such correlations would necessarily lead to poorer system performance.
This could be tested by presenting a fraction of the volunteers with a version
of the site that actively suggested that they take this approach, and then
tracking the relative performance of ``collaborative'' classifications
compared with independent ones. We leave this to further work.

Mistakes by both high and low skill classifiers could be reduced by improving
the training in the system, which could be done in several ways. One is to 
make more training images available to those who want or need it. A basic
level of training images are needed for SWAP to build up an accurate picture
of each classifier's skill -- but one could imagine volunteers {\it choosing}
to see more training images (still at random) in their stream. Another could
be to provide more information about what lenses do. In this project, the
Spotter's Guide was always available on the site, but as a passive background
resource. We might consider providing more links to this guide in the feedback
messages shown to the classifiers as they go -- or perhaps extending these
messages to themselves include more explanations and example images.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
\caption{Stage 2 agent properties, separating veterans from stage 1 from new
volunteers. Point size represents total information generated, dashed lines
are drawn at the mean values for each sample.}
\label{fig:discuss:performance:stage1vstage2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Some trajectories show signs of a random walk problem. Those subjects are
simply ``unlucky:'' they are only seen by low skill classifiers, and  happen
to be mis-classified  enough times to cross the retirement threshold (in the
case of the false negatives) or remain in the system (in the case of the false
positives). While improved training will help reduce this effect, it is here
that targeted task assignment could help improve system performance. We
advertised stage 2 of the current project to all registered users; it was
taken up by stage 1 veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since stage 2 was quite short): of
the 1964 volunteers who took part in the stage 2 classification round, only
774 were veterans from stage 1. \Fref{fig:discuss:performance:stage1vstage2}
shows how the stage 1 skill maps on to stage 2 skill and contribution...

\todo{Phil}{Remake figure to show stage 2 skill vs stage 1 skill with point
size given by stage 2 contribution. Stage 2 newbies will all have 0 +/- small
stage 1 skill. Then move this figure to here.}

Thsi figure suggests that there may be some benefit to opening stage 2 on the
basis of agent skill, in order to reduce the noise in the system generated by
new and low skill volunteers in this more difficult classification stage. A
simple implementation of this would be to switch the web app to the stage 2
version when either a certain stage 1 skill (and/or effort) threshold was
passed. Good strategy would probably be to switch back to stage 1 after some
number of stage 2 classifications (to avoid losing the high skill users from
stage 1 entirely), and also to make it very clear which stage the classifier
was at (since stage 2 requires more careful attention). This is something we
plan to experiment with in future.
